% !TEX root = ../main.tex

\section*{Reviewer \#3}

{\color{red} In the introduction, it should be stressed that there exist other approaches to constrained global optimization, not only metaheuristics. I suggest to mention and discuss briefly some deterministic methods that ensure convergence to the global solution (see... }\\

We included in the introduction a brief description of some deterministic methods cited by the reviewer \#3.


\vspace{1cm}


{\color{red} The paper should be made self-contained by describing solved problems and used methods in detail in such a way that anybody can reproduce the results. Thus, both problems and methods, their parameters, stopping conditions should be described better. In case this takes a lot of space, it is advised to put the required supplementary material in the internet and give the reference to this page. }


\vspace{1cm}


The full statement of all problems was added to the text, as advised by the reviewer.


\vspace{1cm}

{\color{red} It would be desirable to compare the new method with some deterministic algorithms on classes of test functions (e.g. available for free DIRECT algorithm proposed by Jones, Pertunen and Stuckman) following, e.g., the comparing strategy described in in the recent text doi 10.1016/j.amc.2017.\\06.036 However, the reviewer understands that this requires a lot of work and, in case this is difficult, the author can postpone such a comparison in the future work. } \\

We ran C-ITGO in the 800 problems generated by the GKLS class of problems (for 2, 3, 4 and 5 variables, easy and hard cases) and compared the results against some efficient deterministic methods, following the guidelines described in \cite{NAT} for comparing meta-heuristics and deterministic algorithms. All results can be found in the appendix of the C-ITGO paper.

We prefer however to postpone these results in a future paper, given that the whole focus of the current work is about constrained optimization. Also, a considerable part of the paper would have to be devoted to present these results, what would increase the paper length. As a final remark, we also would like to make further improvements to C-ITGO to solve the GKLS class of problems.